---
title: "Coding up StLDA"
author: "Shane Bookhultz"
date: "9/13/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Libraries, echo = F}

suppressWarnings(library("MASS"))

```

## Coding up StLDA

Variables included:

Indices:

* K: The number of topics in a document
* V: The size of the vocabulary to pull from each document
* L: The number of locations (Spatial)
* Y: The number of time points (Temporal)
* P: The number of spatial dimensions

Hyperparameters:

* $\eta$ dirichlet hyperparameter for the concentration of each word in each topic

Parameters:

* $\Omega \in \mathbb{R}^{Y \times L \times K}$ log concentration parameters for the document-topic prevalence 
* $\sigma_w$ isotropic error for matrix AR process on $\Omega$
* $\phi \in \mathbb{R}^{K \times V}$ topic - word probability matrix.
* $w_{y,l,m,n}$ the word in position n of the m'th document at location l at time y.
* $z_{y,l,m,n}$ the topic associated with $w_{y,l,m,n}$
* $\boldsymbol{B}^{L \times L}$ matrix based on distances between the spatial locations divided by a scalar length scale
* $\boldsymbol{A}^{Y \times L \times K}$ matrix based on an AR(1) process



```{r echo = F}
# Actual code of the LDA
set.seed(6787)
# Dummy set up for each variable for the LDA
# Indices/hyperparams
K <- 4
V <- 15
L <- 5
Y <- 10
p <- 3
M <- 10 # Number of documents

eta <- rep(1, times = V)
theta <- 1 #length scale
avgsize <- 6 # Mean words (length) of document


Diri.func <- function(alphavec) {
  simvec <- rgamma(length(alphavec),alphavec,rate = 1)
  rval <- simvec / sum(simvec)
  return (rval)
}

# Parameters

OMEGA <- array(dim=c(Y,L,K))
sigma_m <- 1 # Isotropic error
phi <- matrix(NA, nrow = K, ncol = V)

OMEGA[1,,] <- matrix(rnorm(L*K, mean = 0, sd = sigma_m), nrow = L, ncol = K)


# B is a matrix full of the distances between the l points based off of a kernel of a gaussian

SpatialLocs <- matrix(rnorm(L*p), nrow = L, ncol = p)


B <- exp(-as.matrix(dist(SpatialLocs)/theta))
# B is LxL
# B lower triangular
B[lower.tri(B)] <- 0

for(y in 2:Y) {
  epsilon_t <- matrix(rnorm(L*K,mean = 0, sd = sigma_m),nrow = L, ncol = K)
  OMEGA[y,,] <- B %*% OMEGA[(y-1),,] + epsilon_t
}

A <- array(dim=c(Y,L,K))

for(y1 in 1:Y) {
  A[y1,,] <-  exp(OMEGA[y1,,])
} # I think this is what he means, but the indices on the omega matrix are y-1


# Generating topics (LDA)

for (k in 1:K) {
  phi[k,] <- Diri.func(eta)
}

# Document-Topic prevalence
# Prior on the topic multinomial distribution
priormultiz <- array(dim=c(Y,L,M,K))
# Y temporal points, L spatial points, M documents, K for the dirichlet length

# This is n length of each document, this doesn't take into account location
doclengthvec <- rpois(M,avgsize)

topicarray.z <- array(dim=c(Y,L,M,max(doclengthvec)))
wordarray.w <- array(dim=c(Y,L,M,max(doclengthvec)))

for (y2 in 1:Y) { #Temporal
  for (l in 1:L) { #Spatial
    for(m  in 1:M) { #Each document
      # Create the dirichlet distribution
      
      priormultiz[y2,l,m,] <- Diri.func(A[y2,l,])
      
      for(n in 1:doclengthvec[m]) {
        
        topicarray.z[y2,l,m,n] <- sample(1:K, size = 1, prob = priormultiz[y2,l,m,])
        
        wordarray.w[y2,l,m,n] <- sample(1:V, size = 1, prob = phi[topicarray.z[y2,l,m,n],])
      }
    }
  }
}

```
